### 2024-03-31 tesis_Ashish/Chapter5/chapter5.tex
update 1 April

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb. The bunch to bunch variation and scan to scan variation of the PCC visible cross section is shown in Fig. \ref{fig:period_bound_99} and Fig. \ref{fig:period_bound_105} \cite{pas_22}. %\cite{bril2023vdmrecalibration}.

@@

>>>>

%Background subtraction and beam corrections have been applied to the raw data to account for noise.
%Chi2/ndof for all vdM and Imaging Scans:
%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit. A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit. The variation of $\chi^2$/ndof across scans is shown in Fig. \ref{fig:period_bound_510}. From this plot, we can observe that the average fit quality of the data to the model, as measured by the chi-squared per degree of freedom (chi2/ndof), is slightly above the ideal value of 1, with a mean of approximately 1.55. This suggests that the model fits the data reasonably well overall, but there may be some systematic deviation. The consistency of fit quality across different scans, both X and Y, indicates that no significant discrepancy exists between these two scanning directions within the range of values presented.  The change in beam overlap width across scans is shown in Fig. \ref{fig:period_bound_520}. The plot reveals an asymmetry in beam overlap widths, with the X-Scans showing higher CapSigma values than the Y-Scans in all scans, indicating a larger beam width along the X-axis. The Y-Scans exhibit narrower and more uniform widths, suggesting a more stable overlap along the Y-axis. This consistent difference in the overlap widths between the X and Y scans is evident across various vdM and beam imaging scans.The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb. The bunch to bunch variation and scan to scan variation of the PCC visible cross section is shown in Fig. \ref{fig:period_bound_99} and Fig. \ref{fig:period_bound_105} \cite{pas_22}. %\cite{bril2023vdmrecalibration}.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/DGConst_chi2.jpeg}
\caption{%                                                                                                                                                                  
  $\chi^2$/ndof for all vdM and imaging scans.
}
\label{fig:period_bound_510}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/DGConst_CapSigma.jpeg}
\caption[Beam overlap widths]{%

  Beam overlap widths for each vdM and imaging scans.
}
\label{fig:period_bound_520}
\end{figure}

### 2024-03-31 tesis_Ashish/Chapter7/chapter7.tex
update 1 April

\begin{table}[H]
  \centering
  \caption[dr offset values for two-fold in $\phi$]{dr mean values (mm) obtained from fit for two fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values for two-fold in $\phi$]{dr cut values (mm) for two fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[d$\phi$ cut values for two-fold in $\phi$]{d$\phi$ cut values for two fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
    %-2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
    %-3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
    %-4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
    1  & 0.00088  & 0.0013   & 0.0015    & 0.0016   & 0.0017   \\
    2  & 0.00076   & 0.0011   & 0.0013   & 0.0014   & 0.0015   \\
    3  & 0.00068  & 0.00097  & 0.0012   & 0.0013   & 0.0013   \\
    4  & 0.00061  & 0.00088  & 0.0010   & 0.0011   & 0.0012   \\
  \end{tabular}
  \label{tab:mdphi_cuts_values}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
\caption[Map Of Two Fold Coincidences in $\phi$]{%                                                                                                            
   X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
}
\label{fig:cluster_ring_720}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr_2.png}
\caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%                                                                                                                                                                                      
   X-Y map of reconstructed two-fold coincidences in r using the selections described in the text. We have only reconstructed coincidences in r arising from module overlap in L1L2 and L3L4. The gaps in the plot correspond to other types of two fold coincidences in r that will arise from module overlap in L1L4, L3L4 and L2L3.
}
\label{fig:cluster_ring_79}
\end{figure}

>>>>

\begin{table}[H]
  \centering
  \caption[dr offset values for two-fold in $\phi$]{dr mean values (mm) obtained from fit for two-fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values for two-fold in $\phi$]{dr cut values (mm) for two-fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[d$\phi$ cut values for two-fold in $\phi$]{d$\phi$ cut values for two-fold coincidences in $\phi$ for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
    %-2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
    %-3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
    %-4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
    1  & 0.00088  & 0.0013   & 0.0015    & 0.0016   & 0.0017   \\
    2  & 0.00076   & 0.0011   & 0.0013   & 0.0014   & 0.0015   \\
    3  & 0.00068  & 0.00097  & 0.0012   & 0.0013   & 0.0013   \\
    4  & 0.00061  & 0.00088  & 0.0010   & 0.0011   & 0.0012   \\
  \end{tabular}
  \label{tab:mdphi_cuts_values}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
\caption[Map Of two-fold coincidences in $\phi$]{%                                                                                                            
   X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
}
\label{fig:cluster_ring_720}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr_2.png}
\caption[L1L2 and L3L4 module overlap map for two-fold coincidences in r]{%                                                                                                                                                                                      
   X-Y map of reconstructed two-fold coincidences in r using the selections described in the text. We have only reconstructed coincidences in r arising from module overlap in L1L2 and L3L4. The gaps in the plot correspond to other types of two fold coincidences in r that will arise from module overlap in L1L4, L3L4 and L2L3.
}
\label{fig:cluster_ring_79}
\end{figure}
